---
title: "LinkedIn Data Analysis"
author: "Jake Rozran"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

<style>
body{
  font-family: 'Oxygen', sans-serif;
  font-size: 16px;
  line-height: 24px;
}

h1,h2,h3,h4 {
  font-family: 'Raleway', sans-serif;
}

.container { width: 1000px; }
h3 {
  background-color: #D4DAEC;
  text-indent: 100px; 
}
h4 {
  text-indent: 100px;
}

g-table-intro h4 {
  text-indent: 0px;
}
</style>

---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
library(kableExtra)
library(knitr)
library(scales)

dat <- read.csv("data/raw/Connections.csv")
dat$Connected.On <- as.Date(dat$Connected.On, format = "%d %b %Y")

first_connection <- paste(dat$First.Name[dim(dat)[1]],
                          dat$Last.Name[dim(dat)[1]])
```

# Total Connections Over Time

I currently have **`r dim(dat)[1]`** connections. My first connection was made 
on `r format(min(dat$Connected.On), "%B %d, %Y")` to `r first_connection`. 

```{r total_connections_over_time, echo = FALSE, out.width = "100%", message = FALSE, warning = FALSE}
plot_dat <- dat %>% 
    group_by(Connected.On) %>% 
    summarise(connections = length(Connected.On)) %>% 
    arrange(Connected.On) %>% 
    mutate(cumulative = cumsum(connections))

ggplot(plot_dat, aes(x = Connected.On, y = cumulative)) +
    geom_area(fill = "navy") + 
    xlab("Connection Date") + 
    ylab("Total Connections") +
    theme(panel.background = element_blank(), 
          panel.grid.major.y = element_line(color = "light gray"),
          panel.grid.minor.x = element_line(color = "light gray"),
          panel.grid.major.x = element_line(color = "light gray"),
          axis.ticks.x = element_blank(),
          axis.ticks.y = element_line(color = "light gray"), 
          axis.text = element_text(color = "black", size = 12),
          legend.position = "none")
```

# Most Connections in a Single Day

In my most connected day, 
`r format(plot_dat$Connected.On[plot_dat$connections == max(plot_dat$connections)], "%B %d, %Y")`, 
I connected with **`r max(plot_dat$connections)`** people!  

Here is the table of awesome people who I connected with on that fateful day: 

```{r big_connection, echo = FALSE, out.width = "100%", message = FALSE, warning = FALSE}
tbl_dat <- dat[dat$Connected.On == plot_dat$Connected.On[
    plot_dat$connections == max(plot_dat$connections)], ]
tbl_dat$Email.Address <- NULL
names(tbl_dat) <- gsub("\\.", " ", names(tbl_dat))

kbl(tbl_dat, row.names = FALSE) %>% 
            kable_styling(bootstrap_options = c("striped", "condensed"))
```

# Companies with Most Connections

```{r companies, echo = FALSE, out.width = "100%", message = FALSE, warning = FALSE}
dat$Company <- ifelse(dat$Company == "", "NO COMPANY NAMED", dat$Company)

companies <- dat %>% 
    group_by(Company) %>% 
    summarise(people = length(Company)) %>% 
    arrange(-people) %>% 
    filter(people >= 5)
```

Here are all the companies to which I am connected with 5 or more people:

```{r table, echo = FALSE, out.width = "100%", message = FALSE, warning = FALSE}

kbl(companies, row.names = FALSE) %>% 
            kable_styling(bootstrap_options = c("striped", "condensed"))
```

# CEOs I Know

Some of my connections have quite impressive titles. 
**`r dim(dat[grepl("CEO", dat$Position), ])[1]`** connections have a title of 
CEO!

Here's that list: 

```{r ceos, echo = FALSE, out.width = "100%", message = FALSE, warning = FALSE}
tbl_dat <- dat[grepl("CEO", dat$Position), ]
tbl_dat$Email.Address <- NULL
names(tbl_dat) <- gsub("\\.", " ", names(tbl_dat))

kbl(tbl_dat, row.names = FALSE) %>% 
            kable_styling(bootstrap_options = c("striped", "condensed"))
```

# Data People I Know

Now... data is what I'm all about. Who do I know that has data in their 
title? **`r dim(dat[grepl("data", tolower(dat$Position)), ])[1]`** 
connections have data in their title.

Here's that list: 

```{r data_peeps, echo = FALSE, out.width = "100%", message = FALSE, warning = FALSE}
tbl_dat <- dat[grepl("data", tolower(dat$Position)), ]
tbl_dat$Email.Address <- NULL
names(tbl_dat) <- gsub("\\.", " ", names(tbl_dat))
tbl_dat <- tbl_dat[order(tbl_dat$Company, tbl_dat$`Last Name`, 
                         tbl_dat$`First Name`), ]

kbl(tbl_dat, row.names = FALSE) %>% 
            kable_styling(bootstrap_options = c("striped", "condensed"))
```

# DevOps People I Know

Now... data is what I'm all about. Who do I know that has data in their 
title? **`r dim(dat[grepl("devops", tolower(dat$Position)), ])[1]`** 
connections have data in their title.

Here's that list: 

```{r devops_peeps, echo = FALSE, out.width = "100%", message = FALSE, warning = FALSE}
tbl_dat <- dat[grepl("devops", tolower(dat$Position)), ]
tbl_dat$Email.Address <- NULL
names(tbl_dat) <- gsub("\\.", " ", names(tbl_dat))
tbl_dat <- tbl_dat[order(tbl_dat$Company, tbl_dat$`Last Name`, 
                         tbl_dat$`First Name`), ]

kbl(tbl_dat, row.names = FALSE) %>% 
            kable_styling(bootstrap_options = c("striped", "condensed"))
```